Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-24 doc/om-paper/paper.tex
compositional --> modular.

\title{Compositional Model-Checking for Fault-Tolerant Distributed System Implementations}
\author{Ben and Lee}

@@

The first step in realizing this vision, however, and the one we address in this paper, is to develop an intermediate representation (IR) for the DSL to target when generating formal models. Our target for the IR is one supported by infinite-state model-checking. With proof techniques like IC3~\cite{} and $k$-induction~\cite{}, model-checking scales further than ever before. We envision an IR that allows for specifying system behavior, assumptions, and requirements, but also includes invariants that can be systematically generated by the DSL. Finally, the IR must support easy refactoring and modifications to the design. Making small changes to system specification---for example, modifying the fault model---should require only localized changes to the IR representation, including proofs. In short, the IR should be compositional.

In this work, we combine a number of ideas known in the literature and folklore to build scalable and compositional formal models of fault-tolerant distributed systems. We describe a generic formal model for fault-tolerant distributed systems that aims to reduce the need for ad-hoc verification abstractions and optimizations while maintaining scalability in Section~\ref{sec:model}. There are three aspects of the model: (1) \emph{calendar automata}, originally developed by Dutertre and Sorea~\cite{cal} for specifying real-time systems; (2) \emph{synchronous observers}, originally from the synchronous languages community~\cite{} and more recently popularized by Rushby for model-checking; and (3) \emph{abstract state machines} for abstracting complex systems.

>>>>

\title{Modular Model-Checking for Fault-Tolerant Distributed System Implementations}
\author{Ben and Lee}

@@

The first step in realizing this vision, however, and the one we address in this paper, is to develop an intermediate representation (IR) for the DSL to target when generating formal models. Our target for the IR is one supported by infinite-state model-checking. With proof techniques like IC3~\cite{} and $k$-induction~\cite{}, model-checking scales further than ever before. We envision an IR that allows for specifying system behavior, assumptions, and requirements, but also includes invariants that can be systematically generated by the DSL. Finally, the IR must support easy refactoring and modifications to the design. Making small changes to system specification---for example, modifying the fault model---should require only localized changes to the IR representation, including proofs. In short, the IR should be modular.

In this work, we combine a number of ideas known in the literature and folklore to build scalable and modular formal models of fault-tolerant distributed systems. We describe a generic formal model for fault-tolerant distributed systems that aims to reduce the need for ad-hoc verification abstractions and optimizations while maintaining scalability in Section~\ref{sec:model}. There are three aspects of the model: (1) \emph{calendar automata}, originally developed by Dutertre and Sorea~\cite{cal} for specifying real-time systems; (2) \emph{synchronous observers}, originally from the synchronous languages community~\cite{} and more recently popularized by Rushby for model-checking; and (3) \emph{abstract state machines} for abstracting complex systems.
